---
title: "Data Request: 2018-12-18_Kaysay_23"
output: 
  html_notebook:
    theme: cerulean
    highlight: zenburn
---

# Setup

## Load Useful Libraries

```{r}
library(dplyr)
library(knitr)
library(kableExtra)
```

## Load Useful Variables

```{r}
# Mostly REDCap API tokens
source("~/Desktop/config.R")
```

```{r}
# Helper function for collapse IVP/FVP/TVP field values
## Uses rlang non-standard evalution
collapse_ift_cols <- function(df, col_i) {
  col_i_enquo <- enquo(col_i) # col : expr => quosure
  
  col_i_quoname <- quo_name(col_i_enquo)          # col_i : quosure => string
  col_f_quoname <- paste0("fu_", col_i_quoname)   # col_f : string => string
  col_t_quoname <- paste0("tele_", col_i_quoname) # col_t : string => string
  
  col_f_enquo <- enquo(col_f_quoname) # col_f : string => quosure
  col_t_enquo <- enquo(col_t_quoname) # col_t : string => quosure
  
  # IVP, FVP (fu_), and TVP (tele_) columns are in df
  if (!is.null(df[[col_i_quoname]]) &
      !is.null(df[[col_f_quoname]]) &
      !is.null(df[[col_t_quoname]])) {
    df %>%
      mutate(!!col_i_enquo := coalesce(df[[col_i_quoname]],
                                       df[[col_f_quoname]],
                                       df[[col_t_quoname]])) %>%
      select(-!!col_f_enquo, -!!col_t_enquo)
  } 
  # IVP and FVP (fu_) columns are in df
  else if (!is.null(df[[col_i_quoname]]) &
           !is.null(df[[col_f_quoname]]) &
            is.null(df[[col_t_quoname]])) {
    df %>%
      mutate(!!col_i_enquo := coalesce(df[[col_i_quoname]],
                                       df[[col_f_quoname]])) %>%
      select(-!!col_f_enquo)
  } 
  # IVP and TVP (tele_) columns are in df
  else if (!is.null(df[[col_i_quoname]]) &
            is.null(df[[col_f_quoname]]) &
           !is.null(df[[col_t_quoname]])) {
    df %>%
      mutate(!!col_i_enquo := coalesce(df[[col_i_quoname]],
                                       df[[col_t_quoname]])) %>%
      select(-!!col_t_enquo)
  }
}
```


# Extract Data

## Set Appropriate Fields

### UDS 3
```{r}
# Form Header
fields_u3_raw_header <- 
  c(
    "ptid"          # header
    , "dob"         # header; to derive visit date age
    , "form_date"   # header; to derive visit date age
  )

# Form IVP A1
fields_u3_raw_ivp_a1 <-
  c(
    "sex"         # ivp_a1
    , "race"        # ivp_a1
    , "handed"      # ivp_a1
    , "educ"        # ivp_a1
    , "maristat"    # ivp_a1
  )

# Form IVP C2
fields_u3_raw_ivp_c2 <-
  c(
    "mocatots"    # ivp_c2; 1f. MOCA TOTAL RAW SCORE - UNCORRECTED
  )

# Form IVP D1
fields_u3_raw_ivp_d1 <-
  c(
    ## Normal cognition
    "normcog"     # ivp_d1; 2. Does the subject have normal cognition?
    ## Dementia
    , "demented"    # ivp_d1; 3. Does the subject meet criteria for dementia?
    , "amndem"      # ivp_d1; 4a. Amnestic multidomain dementia syndrome
    , "pca"         # ivp_d1; 4b. Posterior cortical atrophy syndrome
    , "ppasyn"      # ivp_d1; 4c. Primary progressive aphasia (PPA) syndrome
    , "ftdsyn"      # ivp_d1; 4d. Behavioral variant FTD syndrome
    , "lbdsyn"      # ivp_d1; 4e. Lewy body dementia syndrome
    , "namndem"     # ivp_d1; 4f. Non-amnestic multidomain dementia
    , "mciamem"     # ivp_d1; 5a. Amnestic MCI, single domain (aMCI SD)
    , "mciaplus"    # ivp_d1; 5b. Amnestic MCI, multiple domains (aMCI MD)
    , "mcinon1"     # ivp_d1; 5c. Non-amnestic MCI, single domain (naMCI SD)
    , "mcinon2"     # ivp_d1; 5d. Non-amnestic MCI, multiple domains (naMCI MD)
    , "impnomci"    # ivp_d1; 5e. Cognitively impaired, not MCI
    ## Dementia etiology
    , "alzdis"      # ivp_d1; 11. Alzheimer's disease
    , "alzdisif"
    , "lbdis"       # ivp_d1; 12. Lewy body disease
    , "lbdif"
    , "msa"         # ivp_d1; 13. Multiple system atrophy
    , "msaif"
    , "cvd"         # ivp_d1; 15. Vascular Brain injury
    , "cvdif"
    , "esstrem"     # ivp_d1; 16. Essential tremor
    , "esstreif"
    , "downs"       # ivp_d1; 17. Down syndrom
    , "downsif"
    , "hunt"        # ivp_d1; 18. Huntington's disease
    , "huntif"
    , "prion"       # ivp_d1; 19. Prion disease
    , "prionif"
    , "brninj"      # ivp_d1; 20. Traumatic brain injury
    , "brninjif"
    , "hyceph"      # ivp_d1; 21. Normal-pressure hydrocephalus
    , "hycephif"
    , "epilep"      # ivp_d1; 22. Epilepsy
    , "epilepif"
    , "neop"        # ivp_d1; 23. CNS neoplasm
    , "neopif"
    , "hiv"         # ivp_d1; 24. Human immunodeficiency virus
    , "hivif"
    , "othcog"      # ivp_d1; 25. Cognitive impairment due to other not listed
    , "othcogif"
    , "dep"         # ivp_d1; 26. Active depression
    , "depif"
    , "bipoldx"     # ivp_d1; 27. Bipolar disorder
    , "bipoldif"
    , "schizop"     # ivp_d1; 28. Schizophrenia or other psychosis
    , "schizoif"
    , "anxiet"      # ivp_d1; 29. Anxiety disorder
    , "anxietif"
    , "delir"       # ivp_d1; 30. Delirium
    , "delirif"
    , "ptsddx"      # ivp_d1; 31. Post-traumatic stress disorder (PTSD)
    , "ptsddxif"
    , "othpsy"      # ivp_d1; 32. Other psychiatric disease
    , "othpsyif"
    , "alcdem"      # ivp_d1; 33. Cognitive impairment due to alcohol abuse
    , "alcdemif"
    , "impsub"      # ivp_d1; 34. Cognitive imp. due to other substance abuse
    , "impsubif"
    , "dysill"      # ivp_d1; 35. Cognitive impairment due to systemic disease
    , "dysillif"
    , "meds"        # ivp_d1; 36. Cognitive impairment due to medications
    , "medsif"
    , "cogoth"      # ivp_d1; 37. Cognitive impairment NOS
    , "cogothif"
    , "cogoth2"     # ivp_d1; 38. Cognitive impairment NOS
    , "cogoth2f"
    , "cogoth3"     # ivp_d1; 39. Cognitive impairment NOS
    , "cogoth3f"
  )

# Form FVP A1
fields_u3_raw_fvp_a1 <-
  c(
    "fu_sex"      # fvp_a1
    , "fu_maristat" # fvp_a1
  )

# Form TVP A1
fields_u3_raw_tvp_a1 <-
  c(
    "tele_sex"    # tvp_a1
    , "tele_maristat" # tvp_a1
  )

# Append `fu_` and `tele_` to appropriate fields
fields_u3_raw <- c(fields_u3_raw_header
                   , fields_u3_raw_ivp_a1
                   , fields_u3_raw_fvp_a1
                   , fields_u3_raw_tvp_a1
                   , fields_u3_raw_ivp_c2
                   , fields_u3_raw_ivp_d1
                   , paste0("fu_", fields_u3_raw_ivp_c2)
                   , paste0("fu_", fields_u3_raw_ivp_d1)
                   , paste0("tele_", fields_u3_raw_ivp_d1))


# Collapse fields for REDCap API request
fields_u3 <- fields_u3_raw %>% paste(collapse = ",")
```

### MiNDSet Registry
```{r}
fields_ms_raw <- 
  c(
    "subject_id"   # registration_form
    , "exam_date" # medical_visit_form
    , "county"     # patient_demographic_entry
  )
# Collapse fields for REDCap API request
fields_ms <- fields_ms_raw %>% paste(collapse = ",")
```

## Fetch Data via REDCap API

JSON => data.frame => tibble

### UDS 3
```{r}
json_u3 <- rc_api_get(uri    = REDCAP_API_URI,
                      token  = REDCAP_API_TOKEN_UDS3,
                      fields = fields_u3,
                      raw    = TRUE)
df_u3 <- jsonlite::fromJSON(json_u3) %>% as_tibble()
```

### MiNDSet Registry
```{r}
json_ms <- rc_api_get(uri    = REDCAP_API_URI,
                      token  = REDCAP_API_TOKEN_MINDSET,
                      fields = fields_ms,
                      raw    = TRUE)
df_ms <- jsonlite::fromJSON(json_ms) %>% as_tibble()
```

## Save Raw Data As CSV

### UDS 3
```{r}
readr::write_csv(df_u3, "df_u3.csv", na = "")
```

### MiNDSet
```{r}
readr::write_csv(df_ms, "df_ms.csv", na = "")
```

# Transform Data

## Clean Data

### UDS 3
```{r}

```

### MiNDSet Registry
```{r}

```


## Collapse IVP, FVP, TVP Columns

Given columns "bar", "fu_bar", and "tele_bar", we will collapse all the values from those three columns into one column with the base name "bar".

```{r}
# Copy the UDS 3 data frame
df_u3_collapsed <- df_u3

# Define which fields have "fu_" and "tele_" counterparts
ift_fields_collapsible <- c("sex", "maristat", 
                            fields_u3_raw_ivp_c2,
                            fields_u3_raw_ivp_d1)

# Loop over each collapsible field, and do the collapsing
for (field in ift_fields_collapsible) {
  df_u3_collapsed <- collapse_ift_cols(df_u3_collapsed, !!field)
}

readr::write_csv(df_u3_collapsed, "df_u3_collapsed.csv", na = "")
```



# Write Data
